Mergeable Types

### 2017-02-27 paper/related.tex
edits

>>>>

There have been numerous proposals over the years for realizing
distributed functionality in a functional programming context.
Poly/ML~\cite{Mat97} and Facile~\cite{TLK+97} both extend Standard ML
with distributed programming abstractions.  Kali-Scheme~\cite{CJK95}
defines a distributed extension for Scheme-48, and Cloud
Haskell~\cite{EPPJ11} describes a domain-specific language that
enables development of distributed Haskell programs.
Obliq~\cite{Car95} explores issues related to mobility, lexical
scoping, and network references in an object-oriented framework that
enables safe (i.e., lexical) transmission of closures.  However,
Unlike \name, none of these systems consider issues of object
replication or consistency as central to their programming models.
The realities of modern-day scalable distributed systems, especially
those that are constructed from geographically distributed
participants, dictate that we must necessarily grapple with
consistency issues to achieve any kind of reasonable performance; it
is noteworthy that replication is inherent in many widely-used
distributed system implementations today (e.g.,
Cassandra~\cite{Cassandra} or Dynamo~\cite{Dynamo}), which provide
only weak consistency guarantees.  In this context, we view our
primary contribution as one that provides a principled high-level
approach to framing consistency issues leveraging functional
programming abstractions and techniques that minimizes disruption to
the way programmers structure and reason about their applications,
without compromising efficiency or performance.  Indeed, our semantics
of mergeable types and state versioning has utility in any concurrent
context with non-trivial coordination and synchronization costs, even
without taking distribution or replication into account.
